Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS

### 2022-04-11 outputs/paper/paper.Rmd
update on paper

---
title: "Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS"
subtitle: "An Analysis Based on the Kenya's Demographic and Health Survey in 1998"
author: 
  - Charles Lu
  - Mahak Jain
  - Yujun Jiao
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using data extracted from Kenya’s Demographic and Health Surveys in 1998, this analysis aims to study the Kenyans’ perception of their risk of getting AIDS. By analyzing the age, marital status, number of sex partners, residence, province, and education of the survey’s participants, results show that these factors all have different levels of impact on people’s risk of being infected. R [@citeR] is used in this report to create visualizations for the results. In the future, this report can help scholars to dive deeper into the history of the sexually-transmissible disease, study the correlation between the transmission rate and social backgrounds, and aid the authorities in making governmental or health-related plans. "
header-includes:
  - \usepackage{placeins}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    fig_caption: yes
bibliography: references.bib
thanks: "https://github.com/R300G/paper4_placeholder_name"
---

@@

theme_bw <- 
  options(repr.plot.width=15, repr.plot.height=6)
  ggplot(data = subset(data_prov,(!is.na(survey_answer))),  aes(demographic_info, chances_of_getting_aids, fill = survey_answer)) +labs(fill= "Survey Answers") +
         geom_bar(stat = "identity") + 
         scale_y_continuous(name="Percentage") +
         ggtitle("Survey Participant Distribution for Provinces") +
         scale_x_discrete(name="Province") +
         theme_bw()
```

@@

scatterPlote <- ggplot(datae, aes(demographic_info, chances_of_getting_aids, color = survey_answer)) +labs(color = "Survey Answers") +
  geom_point() + facet_wrap(~gender)+ 
  stat_smooth(aes(group = survey_answer), method = "loess", se = FALSE, lty='dashed') +
  labs(
    title = "Survey Participant Distribution for Education",
    x = "education",
    y = "survey participants",
    fill = NULL
  )+scale_color_brewer(
    palette="Spectral")+
  theme_minimal()+
  theme(
    panel.background = element_blank(),
    axis.text.x = element_text(size=10, angle=60, hjust=1, vjust=1),
    axis.title.y = element_text(size=10, angle = 90),
    axis.text.y = element_text(size=12)
  )
scatterPlote
```

@@

scatterPlot1 <- ggplot(datam, aes(demographic_info, chances_of_getting_aids, color = survey_answer)) +
  geom_point() + facet_wrap(~gender)+
  stat_smooth(aes(group = survey_answer), method = "loess", se = FALSE, lty='dashed') +
  labs(
    title = "Survey Participant Distribution",
    x = "Marital Status",
    y = "survey participants",
    fill = NULL
  )+scale_color_brewer(
    palette="Spectral")+
  theme_minimal()
scatterPlot1

@@

scatterPlot1 <- ggplot(datar, aes(demographic_info, chances_of_getting_aids, color = survey_answer)) +
  geom_point() +  facet_wrap(~gender)+
  stat_smooth(aes(group = survey_answer), method = "lm", se = FALSE, lty='dashed') +
  labs(
    title = "Survey Participant Distribution",
    x = "Residence",
    y = "survey participants",
    fill = NULL
  )+scale_color_brewer(
    palette="Spectral")+
  theme_minimal()
scatterPlot1

@@

# Apendix
```{r agevm, fig.cap="Percentage Distribution of Survey Answers by Age", echo = FALSE,fig.width=8, fig.height=4}

@@

marital_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Female)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
\newpage
# References

>>>>

---
title: "Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS"
subtitle: "An Analysis Based on the Kenya's Demographic and Health Survey in 1998"
author: 
  - Charles Lu
  - Mahak Jain
  - Yujun Jiao
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using data extracted from Kenya’s Demographic and Health Surveys in 1998, this analysis aims to study the Kenyans’ perception of their risk of getting AIDS. By analyzing the age, marital status, number of sex partners, residence, province, and education of the survey’s participants, results show that these factors all have different levels of impact on people’s risk of being infected. R [@citeR] is used in this report to create visualizations for the results. In the future, this report can help scholars to dive deeper into the history of the sexually-transmissible disease, study the correlation between the transmission rate and social backgrounds, and aid the authorities in making governmental or health-related plans. "
header-includes:
  - \usepackage{placeins}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    fig_caption: yes
bibliography: references.bib
thanks: "https://github.com/R300G/Kenya_Demographic_1998"
---

@@

theme_bw <- 
  options(repr.plot.width=15, repr.plot.height=6)
  ggplot(data = subset(data_prov,(!is.na(survey_answer))),  aes(demographic_info, chances_of_getting_aids, fill = survey_answer)) +labs(fill= "Survey Answers") +
         geom_bar(stat = "identity") + 
         scale_y_continuous(name="Percentage") +
         scale_x_discrete(name="Province") +
         theme_bw()
```

@@

scatterPlote <- ggplot(datae, aes(demographic_info, chances_of_getting_aids, color = survey_answer)) +labs(color = "Survey Answers") +
  geom_point() + facet_wrap(~gender)+ 
  stat_smooth(aes(group = survey_answer), method = "loess", se = FALSE, lty='dashed') +
  labs(
    x = "education",
    y = "survey participants",
    fill = NULL
  )+scale_color_brewer(
    palette="Spectral")+
  theme_minimal()+
  theme(
    panel.background = element_blank(),
    axis.text.x = element_text(size=10, angle=60, hjust=1, vjust=1),
    axis.title.y = element_text(size=10, angle = 90),
    axis.text.y = element_text(size=12)
  )
scatterPlote
```

@@

scatterPlot1 <- ggplot(datam, aes(demographic_info, chances_of_getting_aids, color = survey_answer)) +labs(color = "Survey Answers")+
  geom_point() + facet_wrap(~gender)+
  stat_smooth(aes(group = survey_answer), method = "loess", se = FALSE, lty='dashed') +
  labs(
    x = "Marital Status",
    y = "survey participants",
    fill = NULL
  )+scale_color_brewer(
    palette="Spectral")+
  theme_minimal()
scatterPlot1

@@

scatterPlot1 <- ggplot(datar, aes(demographic_info, chances_of_getting_aids, color = survey_answer)) +labs(color = "Survey Answers")+
  geom_point() +  facet_wrap(~gender)+
  stat_smooth(aes(group = survey_answer), method = "lm", se = FALSE, lty='dashed') +
  labs(
    x = "Residence",
    y = "survey participants",
    fill = NULL
  )+scale_color_brewer(
    palette="Spectral")+
  theme_minimal()
scatterPlot1

@@

# Apendix

## Data Visualization
```{r agevm, fig.cap="Percentage Distribution of Survey Answers by Age", echo = FALSE,fig.width=8, fig.height=4}

@@

marital_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Female)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```

## Datasheet

\newpage
# References
